---
title: "info"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4,fig.align = "center") 
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
```

```{r setup}
library(rpackage)
```

# RPackage for MATH 4573

This r package was created for MATH 4573 by Caleb Guinn. This package contains 4 functions and one dataset.

## Functions

The functions in this package are:
-mychisim() a Chi Squared Simulator
-myboot() a simple Bootstrapping function
-mymlbeta() a maximum likelihood calculator
-mycltp() a function that demonstrates the Central Limit Theorem for the Poisson Distribution

### Chi Squared Simulator

You can call the function as it is and the output list will print to console.

```{r}
mychisim(n=10,sigma=4,mean=10,iter=1000,ymax=0.1)
```

Or you can assign the function to an object and the object will contain the list instead, the plot will still be shown.

```{r}
c<-mychisim(n=10,sigma=4,mean=10,iter=1000,ymax=0.1)
```

### Bootstrapping Function

The function creates a bootstrapped sample from the initial sample x. The statistic for the function as well as the type of distribution can be changed to produce different outputs.

#### Example 1

```{r}
set.seed(40)
sam<-rnorm(25,mean=25,sd=10)
myboot(x=sam,fun="mean",iter=10000, xlab="mean",col="Purple")
```

#### Example 2

```{r}
set.seed(40)
sam<-rgamma(30,shape=2,scale=3)
myboot(x=sam,fun="var",iter=10000,xlab="variance", col="Blue",alpha=0.20)
```

#### Example 3

You can also put the function output list to an object so that only the plot is shown:



```{r}
set.seed(40)
sam<-rbeta(30,shape1=2,shape2=3)
b<-myboot(x=sam,fun="median",iter=10000,xlab="median", col="Yellow",alpha=0.20)
```



### Maximum Likelihood Estimator for Beta Distribution

Creates a MLE for the randomly generated beta distribution.

#### Example 1

```{r}
sam<-rbeta(30,shape1=3,shape2=4)
nsam<-length(sam)
mymlbeta(x=sample(sam,nsam,replace=TRUE),alpha=seq(0.1,20,length=100),beta=seq(0.1,20,length=100),lwd=2,labcex=1,col="steelblue")
```

#### Example 2
```{r}
sam<-rbeta(50,shape1=3,shape2=4)
nsam<-length(sam)
m<-mymlbeta(x=sample(sam,nsam,replace=TRUE),alpha=seq(0.1,20,length=100),
beta=seq(0.1,20,length=100),lwd=2,labcex=1,col="red")
```

### Central Limit Theorem for Poisson Distribution

Creates a density histogram of the sample mean for the poisson distribution generated, a frequency barplot of the sampled y, and a probability plot for the function.

#### Example 1

```{r}
mycltp(n=20,iter=10000,lambda=10)
```

#### Example 2

```{r}
mycltp(n=2,iter=10000,lambda=4)
```

#### Example 3

```{r}
p<-mycltp(n=5,iter=10000,lambda=10)
```

#### Example 4

```{r}
p<-mycltp(n=5,iter=10000,lambda=4)
```

## Data

```{r}
head(POWERLOADS)
```

